---
title: "Basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{codedoc_basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Consider this simple R script:

```{r, results = "asis", echo = FALSE}
cat("```R\n")
cat(codedoc::example_text_file_lines("r_script.R"), sep = "\n")
cat("\n```\n")
```

Note the comment blocks starting with `@doc current_age` and `@doc age_group`.
These specify comment blocks that this package can identify as code 
documentation for the purpose of compiling a single aggregated document
(html, pdf, etc. using rmarkdown::render).

Any text after the `@doc` identifier is called the *key* of the comment block.
Keys are used to identify comment blocks when compiling the documentation.
There must be exactly two lines with `@doc my_key` for any key. Otherwise
an error is raised.

You can extract the comment blocks based on this information using
`codedoc::extract_keyed_comment_blocks`. Here we refer to an example text
file stored into this package.

```{r}
key_df <- codedoc::extract_keyed_comment_blocks(
  text_file_paths = codedoc::example_text_file_path("r_script.R")
)
print(key_df$key)
```

```{r}
print(key_df$comment_block)
```

You would usually not use this result directly, but rather render a 
documentation file using it. `codedoc::render_codedoc` is designed to do just
that. You may use a template .rmd to define the structure of your document,
and it's contents will be taken from `key_df` (hence originally from your code).
Here's an example template:

```{r, results = "asis", echo = FALSE}
cat("```R\n")
cat(codedoc::example_template_lines("r_script_template.rmd"), sep = "\n")
cat("\n```\n")
```
Let's now render the document using the above template and the `key_df` 
we created.

```{r}
# we use a temp file just for the purpose of creating this vignette. in your
# case that probably won't be necessary.
tmp_dir_path <- tempdir()
tmp_md_file_path <- tempfile(fileext = ".md")
template_file_path <- codedoc::example_template_file_path("r_script_template.rmd")
codedoc::render_codedoc(
  key_df = key_df, 
  template_file_path = template_file_path,
  render_arg_list = list(output_dir = tmp_dir_path, 
                         output_file = tmp_md_file_path)
)

```

This is what the rendered .md looks like:

```{r, results = "markdown", echo = FALSE}
cat(readLines(tmp_md_file_path), sep = "\n")
```


As you can see, it was populated by the contents of `key_df`.

This concludes the basics of using this package. Happy documenting!


